---
title: "Events"
---

```{r, out.extra= "class='img-right'", echo = FALSE} 
knitr::include_graphics("images/DSC_5760 (2).JPG")
```


There is so much to see and do in this corner of Manitoba!

Events range from casual walks through city parks, to bird watching along rivers and wetlands, to public talks by local experts.

### Current situation {.notice}
While Westman Naturalists are unable to host in-person events at this, we do have some online events, so keep checking back!


```{r, message = FALSE, echo = FALSE}
library(tidyverse)
library(lubridate)
library(glue)
library(googlesheets4)

events <- gs4_get("https://docs.google.com/spreadsheets/d/132krSjS7w574gavkX31XxmcmmafXbC-zfM81W2mDXAY") %>%
  read_sheet() %>%
  mutate(month = month(Start),
         Start = replace(Start, Tentative == "yes", as_datetime(NA)),
         Date = format(Start, "%A, %b %d %Y"),
         Date = replace_na(Date, "TBA"),
         Time = format(Start, "%I:%M %p"),
         Time = replace_na(Time, "TBA"),
         Time = str_replace(Time, "12:00 AM", "All day"),
         Time = str_remove(Time, "^0"),
         Description = str_replace_all(Description, 
                                       "westman.naturalists@gmail.com", 
                                       "[westman.naturalists@gmail.com](mailto:westman.naturalists@gmail.com)"),
         Extra = if_else(Extra != "", glue("<div class = 'notice'>\n\n{Extra}\n\n</div>"), ""),
         Status = if_else(tolower(Status) == "cancelled",
                          "**<span class='notice'>Cancelled</span>** ", ""),
         Footer = if_else(str_detect(Hosted, "Westman Naturalists"), 
                          "[Contact Westman Naturalists for more information](mailto:westman.naturalists@gmail.com)",
                          "Note that this event is not hosted by Westman Naturalists"),
         Hosted = glue("Hosted by {Hosted}"),
         event = glue("{Extra}\n\n",
                      "{Status}<span class = 'date'>{Date}</span>\n\n",
                      "<span class = 'event-title'>{Title}</span>; {Hosted}\n\n",
                      "{Description}\n\n", 
                      "**Time**: {Time}<br>",
                      "**Location**: {Location}\n\n",
                      "{Footer}", .na = ""),
         past = Start < Sys.time(),
         past = replace_na(past, FALSE))
```


## Upcoming Events

Everyone is welcome to join in on any and every event!

Please remember to dress for the weather, bring water and bug spray, and food for outings.
To aid in planning, please let us know if you are attending any of our out of town trips, by [sending the Westman Naturalists an email](mailto:westman.naturalists@gmail.com).



```{r, echo = FALSE, results = "asis"}
upcoming <- filter(events, !past) %>%
  arrange(Start) %>%
  nest(data = c(-month))
  

for(m in upcoming$month) {
  print(glue("\n\n## ", as.character(month(m, label = TRUE, abbr = FALSE)), "\n\n"))
  
  filter(upcoming, month == m) %>%
    unnest(cols = data) %>%
    pull(event) %>%
    glue_collapse(sep = "\n\n-----\n\n") %>%
    print()
}
```


## Previous Events
```{r, echo = FALSE, results = "asis"}
past <- filter(events, past) %>%
  arrange(desc(Start)) %>%
  nest(data = c(-month))

for(m in past$month) {
  print(glue("\n\n## ", as.character(month(m, label = TRUE, abbr = FALSE)), "\n\n"))
  
  filter(past, month == m) %>%
    unnest(cols = data) %>%
    pull(event) %>%
    glue_collapse(sep = "\n\n-----\n\n") %>%
    print()
}
```

