---
title: "Events"
---

::: {.columns}
::::: {.column width=60%}
There is so much to see and do in this corner of Manitoba!

Events range from casual walks through city parks, to bird watching along rivers
and wetlands, to public talks by local experts. Everyone is welcome to join in
on any and every event!

Please remember to dress for the weather and bring appropriate footwear for the
great outdoors! And it never hurts to bring water and snacks (or lunch on our
longer outings). If you take any photos on a trip, send them to us and we'll
share them on social media!

Add our events calendar to your [Google calendar](https://calendar.google.com/calendar/u/0?cid=d2VzdG1hbi5uYXR1cmFsaXN0c0BnbWFpbC5jb20)!
:::::

::::: {.column width=40%}
![](images/DSC_5760 (2).JPG){fig-alt="Pink cactus blooming"}
:::::
:::

```{r}
#| echo = FALSE,
#| results = "asis"
library(dplyr)
library(tidyr)
library(glue)
library(lubridate)

events <- readRDS("events.rds")

upcoming <- filter(events, !.data$past) |>
  arrange(.data$date) |>
  nest(data = c(-"month"))

if (nrow(upcoming) == 0) {
  cat("> **Nothing planned at the moment, but check back!**")
} else {
  for (m in upcoming$month) {
    print(glue(
      "\n\n## ",
      as.character(month(m, label = TRUE, abbr = FALSE)),
      "\n\n"
    ))

    filter(upcoming, .data$month == .env$m) |>
      unnest(cols = "data") |>
      mutate(event = glue("{.data$event}\n\n{.data$post_link}")) |>
      pull(.data$event) |>
      glue_collapse(sep = "\n\n-----\n\n") |>
      print()
  }
}
```

--------------------------------------------------------------------------------

# Previous Events

Take a look back at everything we've done over the years!

```{r}
#| echo = FALSE,
#| results = "asis"
past <- filter(events, .data$past) |>
  arrange(desc(.data$date)) |>
  nest(data = c(-"year", -"month"))

cat(":::{.panel-tabset}\n\n")

for (y in unique(past$year)) {
  cat(glue("\n\n#### {y}\n\n"))

  p <- filter(past, year == y)
  if (nrow(p) > 0) {
    for (i in seq_len(nrow(p))) {
      m <- p$month[i]

      print(glue(
        "\n\n## {as.character(month(m, label = TRUE, abbr = FALSE))} {y}\n\n"
      ))

      p[i, ] |>
        unnest(cols = "data") |>
        mutate(event = glue("{.data$event}\n\n{.data$post_link}")) |>
        pull(.data$event) |>
        glue_collapse(sep = "\n\n-----\n\n") |>
        print()
    }
  }
}
cat("\n\n:::\n\n")
```
